Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon Populations

### 2021-11-04 analysis/paper/paper.Rmd
changed paths to data

---
title: "Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon Populations"
author:
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: true
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: false
  - Nicholas J. Porter:
      email: Nicholas.Porter@merck.com
      institute: [biomark]
      correspondence: false
  - Michael S. Hall:
      email: Mike.Hall1@merck.com
      institute: [biomark]
      correspondence: false
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc., 705 South 8th Street, Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography: 
- references.bib      # Kevin's library
- AckermanLibrary.bib # Mike's library
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
  Abstract text here. 
keywords: |
  northern pikeminnow; Chinook salmon; predation; mark-recapture; bioenergetics
highlights: |
  These are the highlights. 
---

@@

```{r load-libraries}
library(tidyverse)
library(janitor)

```{r set-prefix}
# set NAS prefix, depending on operating system
if(.Platform$OS.type != 'unix') {
  nas_prefix = "S:"
} else if(.Platform$OS.type == 'unix') {
  nas_prefix = "~/../../Volumes/ABS"
}

@@

```{r cmr-effort-data}
cmr_df = read_csv(paste0(nas_prefix, "/data/fish/deadwater/deadwater_cmr_effort_20210614.csv")) %>%
  clean_names()

@@

```{r temp-data}
temp_df = read_delim(paste0(nas_prefix,
                            "/data/temperature/deadwater/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                     delim = "\t",
                     comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

>>>>

---
title: "Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon Populations"
author:
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: true
  - Nicholas J. Porter:
      email: Nicholas.Porter@merck.com
      institute: [biomark]
      correspondence: false
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: false
  - Michael S. Hall:
      email: Mike.Hall1@merck.com
      institute: [biomark]
      correspondence: false
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc., 705 South 8th Street, Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography: 
- references.bib      # Kevin's library
- AckermanLibrary.bib # Mike's library
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
  Abstract text here. 
keywords: |
  northern pikeminnow; Chinook salmon; predation; mark-recapture; bioenergetics
highlights: |
  These are the highlights. 
---

@@

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(janitor)

@@

```{r cmr-effort-data}
cmr_df = read_csv("../data/raw data/deadwater_cmr_effort_20210614.csv") %>%
  clean_names()

@@

```{r shoup-temp-data}
temp_df = read_tsv("../data/raw data/USGS_13307000_Salmon_River_Nr_Shoup.txt",
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)
